Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-04-05 paper.tex
Plot not shown
Move text from conclusion to results

For surface-surface-surface function $F_{sss}$ the former approach can also be
used, but it would be highly inefficient memory-wise because for three
dimensional case $F_{sss}$ is a function of six scalar coordinates which leads
to a very large output array. Instead of this approach we use a slower approach
which computes $F_{sss}$ at a specified point calculating a convolution using
its definition:
\begin{algorithmic}[1]
  \Procedure{surfsurfsurf}{$A$, $\bm{r_1}$, $\bm{r_2}$}
  \State $A' \gets |H*A|$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $A'_1 \gets shift(A', \bm{r_1})$
  \Comment{Shift $A$ in $i$-th dimension by $r_{1i}$ for all $i \in \overline{1, ndim(A)}$}
  \State $A'_2 \gets shift(A', \bm{r_2})$
  \Comment{Shift $A$ in $i$-th dimension by $r_{2i}$ for all $i \in \overline{1, ndim(A)}$}
  \State $M \gets A' \cdot A'_1 \cdot A'_2$
  \Comment{Multiplicate three arrays element-wise}
  \State \textbf{return} $\sum_{i} M_{i} / N$
  \Comment{Sum all elements in $M$ and divide by a number of elements in $A$}
  \EndProcedure
\end{algorithmic}
This algorithm can be vectorized and therefore benefits from the usage of
GPUs. Shift function in this algorithm must be a circular shift which
``rotates'' content of the array, if periodic boundary conditions are
desired. For our purpose we use $F_{sss}$ function in the form
$F_{sss}(r_1, r_2, \theta)$ and fix $\theta = \pi/2$. This leads us to a
sampling pattern shown on \cref{fig:Fsss-pattern}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/pattern.png}
  \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
    implementation is a right triangle with fixed catets $r_1$ and $r_2$.
    Patterns can lie in planes $XY$ (as on the picture), $XZ$ or $YZ$. This
    pattern is moved over the input which results in all possible distinct
    configurations. Black dots depict elements of $A'$.}
  \label{fig:Fsss-pattern}
\end{figure}

>>>>

For surface-surface-surface function $F_{sss}$ the former approach can also be
used, but it would be highly inefficient memory-wise because for three
dimensional case $F_{sss}$ is a function of six scalar coordinates which leads
to a very large output array. Instead of this approach we use a slower approach
which computes $F_{sss}$ at a specified point calculating a convolution using
its definition:
\begin{algorithmic}[1]
  \Procedure{surfsurfsurf}{$A$, $\bm{r_1}$, $\bm{r_2}$}
  \State $A' \gets |H*A|$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $A'_1 \gets shift(A', \bm{r_1})$
  \Comment{Shift $A$ in $i$-th dimension by $r_{1i}$ for all $i \in \overline{1, ndim(A)}$}
  \State $A'_2 \gets shift(A', \bm{r_2})$
  \Comment{Shift $A$ in $i$-th dimension by $r_{2i}$ for all $i \in \overline{1, ndim(A)}$}
  \State $M \gets A' \cdot A'_1 \cdot A'_2$
  \Comment{Multiplicate three arrays element-wise}
  \State \textbf{return} $\sum_{i} M_{i} / N$
  \Comment{Sum all elements in $M$ and divide by a number of elements in $A$}
  \EndProcedure
\end{algorithmic}
This algorithm can be vectorized and therefore benefits from the usage of
GPUs. Shift function in this algorithm must be a circular shift which
``rotates'' content of the array, if periodic boundary conditions are
desired. For our purpose we use $F_{sss}$ function in the form
$F_{sss}(r_1, r_2, \theta)$ and fix $\theta = \pi/2$. This leads us to a
sampling pattern shown on \cref{fig:Fsss-pattern}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/pattern.png}
  \caption[]{Sampling pattern used for calculation of $F_{sss}$ in our
    implementation is a right triangle with varying catets $r_1$ and
    $r_2$. Patterns can lie in planes $XY$ (as on the picture), $XZ$ or
    $YZ$. Black dots depict elements of $A'$}
  \label{fig:Fsss-pattern}
\end{figure}
